---
title: "Loess Trading Strategy On The S&P500 Stock Market Index "
author: "Han Zhang"
date: "Nov 3, 2016"
output: html_document
---

##Source

The trading stragegy is based on the article at <https://www.quantstart.com/articles/ARIMA-GARCH-Trading-Strategy-on-the-SP500-Stock-Market-Index-Using-R>.

The strategy is carried out on a "rolling window" basis:

1. For each day, $n$, the previous $k$ days of the differenced logarithmic returns of a stock market index are used as a window for fitting an optimal local linear regression model with optimal bandwidth.

2. The combined model is used to make a prediction for the next day returns.

3. If the prediction is negative the stock is shorted at the previous close, while if it is positive it is longed.

4. If the prediction is the same direction as the previous day then nothing is changed.

We will use the maximum available data from Yahoo Finance for the S&P500. I have taken $k=500$ but this is a parameter that can be optimised in order to improve performance or reduce drawdown.

The backtest is carried out in a straightforward vectorised fashion. Hence the performance achieved in a real trading system would likely be slightly less than you might achieve here, due to commission and slippage.

##Strategy Implementation

The first task is to install and import the necessary libraries in R:

```{r, eval=TRUE, include=FALSE}
#install.packages("quantmod")
#install.packages("lattice")
#install.packages("timeSeries")
#install.packages("rugarch")
#install.packages(streamgraph)
#install.packages('viridis')

library("xts") #for time series
library("nloptr") #for optimization
library(zoo)
library("dygraphs") #for plots
library("magrittr") # pipes
library(dplyr)
#library(streamgraph)
#library(viridis)

library(quantmod)
library(lattice)
library(timeSeries)
library(rugarch)

```

## Including Plots
We are going to apply the strategy to the S&P500. 
We obtain the data from quantmod. Yahoo Finance uses the symbol "^GPSC".

```{r}
#getSymbols("^GSPC", from="2004-01-01",to="2016-11-01")
load("C:/Users/zhang/Desktop/STAT GU4263/GSPC.RData")
```

We create the differenced logarithmic returns of the "Closing Price" of the S&P500 and strip out the initial NA value:

```{r}
spReturns = diff(log(Cl(GSPC)))
spReturns[as.character(head(index(Cl(GSPC)),1))] = 0
```

We need to create a vector, forecasts to store our forecast values on particular dates. 
We set the length foreLength to be equal to the length of trading data we have minus $k$, the window length:

```{r}
windowLength <- 500
foreLength <- length(spReturns) - windowLength
forecasts <- matrix(NA,foreLength+1,2)
```



```{r, eval=FALSE, include=TRUE}
if (1==1)
{
  for (d in 0£ºforeLength) {
    spReturnsOffset = spReturns[(1+d):(windowLength+d)]
r1<-as.vector(spReturnsOffset[3:496])#vector hold values of rt-1
r2<-as.vector(spReturnsOffset[2:495])
r3<-as.vector(spReturnsOffset[1:494])
r<-as.vector(spReturnsOffset[4:497])
data_r<-as.data.frame(cbind(r1,r2,r3,r))#data for fit

#data for predict
r11<-as.vector(spReturnsOffset[497:499])
r22<-as.vector(spReturnsOffset[496:498])
r33<-as.vector(spReturnsOffset[495:497])

predict_r<-as.data.frame(cbind(r11,r22,r33))
colnames(predict_r)<-c('r1','r2','r3')
#3. Fit the loess model
final.FMSE <- Inf
final.bandwidth <- 0
spanlist<-c(seq(from=0.1,to=2,by=0.1))#generate a list of h from 0.1 to 2

#pick h that minimizes FMSE
for (i in 1:length(spanlist)) 
{
  
  
  y.loess = tryCatch( loess(r ~ r1+r2+r3, data_r, span=spanlist[i]),
                       error=function( err ) FALSE,
                       warning=function( err ) FALSE )
  #4. if we got the fit return update the FMSE else move to the next model.
  if( !is.logical( y.loess ) ) {
    y.predict <- predict(y.loess, predict_r) #get predict value of y
    #compute FMSE
    currentFMSE<-sum((y.predict-spReturnsOffset[498:500])^2)
    currentFMSE<-sqrt(1/3*currentFMSE)
     #if current FMSE=NA for a rolling window?
    
    if ((!is.na(currentFMSE)) & (currentFMSE < final.FMSE)) {
      final.FMSE <- currentFMSE
      final.bandwidth <- spanlist[i]
     
    }
  } else {
    next
  }
}
#dont get any bandwidth since all value of current FMSE is NA,set the direction to long
if(final.bandwidth==0){
  forecasts[d+1,1] = index(spReturnsOffset)[windowLength]
        forecasts[d+1,2] = 1
        print("warning or error")
        print(paste(paste('Date: ',index(spReturnsOffset)[windowLength],sep=''), paste(' Signal = ',1,sep=''),paste(' Progress = ',paste(round(10000*d/foreLength)/100,'%',sep=''),sep=''), sep=";")) 
}



else{
r111<-as.vector(spReturnsOffset[3:499])#vector hold values of rt-1
r222<-as.vector(spReturnsOffset[2:498])
r333<-as.vector(spReturnsOffset[1:497])
r444<-as.vector(spReturnsOffset[4:500])
final_r<-as.data.frame(cbind(r111,r222,r333,r444))#data for fit
colnames(final_r)<-c('r1','r2','r3','r')
finaly.loess <- loess(r ~ r1+r2+r3, final_r, span=final.bandwidth)


# choose the correct forecast direction based on the returns prediction
# Output the results to the screen and the forecasts vector
usepredict<-cbind.data.frame(as.vector(spReturnsOffset[500]),as.vector(spReturnsOffset[499]),as.vector(spReturnsOffset[498]))
colnames(usepredict)<-c('r1','r2','r3')
fore<-predict(finaly.loess, usepredict)
#if forecast is NA,set the direction to be one( missing some value in 498 499 500 of rolling window)
if(is.na(fore)){
  forecasts[d+1,1] = index(spReturnsOffset)[windowLength]
        forecasts[d+1,2] = 1
        print("warning or error")
        print(paste(paste('Date: ',index(spReturnsOffset)[windowLength],sep=''), paste(' Signal = ',1,sep=''),paste(' Progress = ',paste(round(10000*d/foreLength)/100,'%',sep=''),sep=''), sep=";")) 
}
  #10 compute the one-step-ahead forecast and store the trading decision {-1,1}
else{
  forecasts[d+1,1] = index(spReturnsOffset)[windowLength]
  forecasts[d+1,2] = ifelse(fore < 0, -1, 1)
  #print the date 
  print(paste(paste('Date: ',index(spReturnsOffset)[windowLength],sep=''), paste(' Signal = ',ifelse(fore < 0, -1, 1),sep=''),paste(' Progress = ',paste(round(10000*d/foreLength)/100,'%',sep=''),sep=''), sep=";")) 
}
}
  
      
}

  
write.csv(forecasts, file="forecasts_prj2.csv", row.names=FALSE,quote=FALSE)

}
```


# Input the CSV file

```{r}
forecastcsv <-read.csv(file="C:/Users/zhang/Desktop/STAT GU4263/forecasts_prj2.csv", header=T, sep=",",dec = ".")
forecastcsv1<-read.csv(file="C:/Users/zhang/Desktop/STAT GU4263/forecasts2.1.csv", header=T, sep=",",dec = ".")
forecastcsv2 <-read.csv(file="C:/Users/zhang/Desktop/STAT GU4263/forecasts_prj1.1noerror.csv", header=T, sep=",",dec = ".")

spArimaGarch2 <- as.xts(forecastcsv$V2,order.by=as.Date(forecastcsv$V1))
spArimaGarch2 <- lag(spArimaGarch2)

spArimaGarch1 <- as.xts(forecastcsv1$V2,order.by=as.Date(forecastcsv1$V1))
spArimaGarch1 <- lag(spArimaGarch1)

spArimaGarch0 <- as.xts(forecastcsv2$V2,order.by=as.Date(forecastcsv2$V1))
spArimaGarch0 <- lag(spArimaGarch0)
```

# Create the Loess method,neural network and ARMA-GARCH returns

```{r}

spIntersect         <- merge( spArimaGarch2[,1], spReturns)
spArimaGarchReturns <- spIntersect[,1] * spIntersect[,2]

spIntersect1         <- merge( spArimaGarch1[,1], spReturns)
spArimaGarchReturns1 <- spIntersect1[,1] * spIntersect1[,2]

spIntersect2         <- merge( spArimaGarch0[,1], spReturns)
spArimaGarchReturns2 <- spIntersect2[,1] * spIntersect2[,2]

```

# Create the backtests for ARIMA+GARCH and Loess method and neural network

```{r}

#merge the three time series of returns
spCombined <-merge(spArimaGarchReturns,spArimaGarchReturns1,all=F)
spCombined <-merge(spCombined,spArimaGarchReturns2,all=F)
spCombined<-merge(spCombined,spIntersect[,2],all=F)
#exclude NA and compute cumulative log-returns 
spCombinedCurve   <-(1+cumsum(na.exclude(spCombined)))

```

# Plot the four time series of cumulative returns on one figure

```{r}
colnames(spCombinedCurve)<-c("Loess Method","Arma-Garch","Neural Network","Buy&Hold")
dygraph(spCombinedCurve) %>%
  dyRangeSelector()  %>% 
  dyOptions(axisLineWidth = 1.5, fillGraph = FALSE, drawGrid = FALSE, rightGap=50)
Loess_returns<-spArimaGarchReturns
colnames(Loess_returns)<-("S_P_ratio_Loess")
Sharpe_Ratio_Loess<-sqrt(252)*(mean(Loess_returns,na.rm=T)/sd(Loess_returns,na.rm=T))
Sharpe_Ratio_Arma_Garch<-sqrt(252)*(mean(spArimaGarchReturns1,na.rm=T)/sd(spArimaGarchReturns1,na.rm=T))
```

#Report Sharpe Ratio of Loess Method
```{r}
Sharpe_Ratio_Loess
```

#Report Sharpe Ratio of Buy and Hold
```{r}
Sharpe_Ratio_BuyandHold<-(mean(spIntersect[501:3232,2],na.rm=T)/sd(spIntersect[501:3232,2],na.rm=T))*sqrt(252)
Sharpe_Ratio_BuyandHold
```

#Report Sharpe Ratio of Neural Network
```{r}
Sharpe_Ratio_Neural_Network<-sqrt(252)*(mean(spArimaGarchReturns2,na.rm=T)/sd(spArimaGarchReturns2,na.rm=T))
Sharpe_Ratio_Neural_Network
```

#Report Sharpe Ratio of ARMA-GARCH
```{r}
Sharpe_Ratio_Arma_Garch
```

#Since the cumulative returns of ARMA-GARCH and Sharpe Ratio of Arma Garch are both higher, ARMA-GARCH is a better strategy. And loess method has the lowest cumulative return and sharpe ratio among the four methods. 
