---
title: "Project.Neural Network Trading Strategy On The S&P500 Stock Market Index "
author: "Han Zhang" 
date: "Nov 3, 2016"
output: html_document
---

##Source

This R Markdown document is based on the article at <https://www.quantstart.com/articles/ARIMA-GARCH-Trading-Strategy-on-the-SP500-Stock-Market-Index-Using-R>.

The strategy is carried out on a "rolling window" basis:

1. For each day, $n$, the previous $k$ days of the differenced logarithmic returns of a stock market index are used as a window for fitting an optimal Neural Network model.

2. The combined model is used to make a prediction for the next day returns.

3. If the prediction is negative the stock is shorted at the previous close, while if it is positive it is longed.

4. If the prediction is the same direction as the previous day then nothing is changed.

We will use the maximum available data from Yahoo Finance for the S&P500. I have taken $k=500$ but this is a parameter that can be optimised in order to improve performance or reduce drawdown.

The backtest is carried out in a straightforward vectorised fashion. Hence the performance achieved in a real trading system would likely be slightly less than you might achieve here, due to commission and slippage.

##Strategy Implementation

The first task is to install and import the necessary libraries in R:

```{r, eval=TRUE, include=FALSE}
install.packages("quantmod")
install.packages("lattice")
install.packages("timeSeries")
install.packages("rugarch")
install.packages(streamgraph)
install.packages('viridis')
install.packages('neuralnet')

library("xts") #for time series
library("nloptr") #for optimization
library(zoo)
library("dygraphs") #for plots
library("magrittr") # pipes
library(dplyr)
library(streamgraph)
library(viridis)

library(quantmod)
library(lattice)
library(timeSeries)
library(rugarch)
library(neuralnet)
```

## Including Plots
We are going to apply the strategy to the S&P500. 
We obtain the data from quantmod. Yahoo Finance uses the symbol "^GPSC".

```{r}
getSymbols("^GSPC", from="2004-01-01",to="2016-11-01")
#load("C:/Users/zhang/Desktop/STAT GU4263/hw4/GSPC.RData")
```

We create the differenced logarithmic returns of the "Closing Price" of the S&P500 and strip out the initial NA value:

```{r}
spReturns = diff(log(Cl(GSPC)))
spReturns[as.character(head(index(Cl(GSPC)),1))] = 0
```

We need to create a vector, forecasts to store our forecast values on particular dates. 
We set the length foreLength to be equal to the length of trading data we have minus $k$, the window length:

```{r}
windowLength <- 500
foreLength <- length(spReturns) - windowLength
forecasts <- matrix(NA,foreLength+1,2)
```


```{r}
P=5
Q=5
nnAll=matrix(list(),P,Q+1)



nnAR3 <- function(data1,p,q,weights)
{
  T1 <- dim(data1)[1]
  maxs <- apply(data1, 2, max) 
  mins <- apply(data1, 2, min)
  scaled <- as.data.frame(scale(data1, center = mins, scale = maxs - mins))
  
  Y <- scaled[4:T1,1]
  X <- c(scaled[3:(T1-1),1],scaled[2:(T1-2),1],scaled[1:(T1-3),1])
  X <- matrix(X,length(X)/3,3)
  
  f  <- as.formula("Y ~ X[,1] + X[,2] + X[,3]")
  if (q>0){
    nn1 <- neuralnet(f,data=scaled,hidden=c(p,q),linear.output=T,startweights=weights)  
  }else #q=0 corresponds to a NN with one hidden layer and p neurons
  {
    nn1 <- neuralnet(f,data=scaled,hidden=p,linear.output=T,startweights=weights)  
  }
  pr.nn   <- compute(nn1,t(c(scaled[T1,1],scaled[(T1-1),1],scaled[(T1-2),1])))
  pr.nn_  <- pr.nn$net.result*( maxs - mins ) + mins
  nn1$pr  <- pr.nn
  nn1$pr_ <- pr.nn_
  
  return(nn1)
}




if (1==1)
{
  for (d in 0:foreLength) {
    spReturnsOffsetnn = spReturns[(1+d):(windowLength+d)]
    T    <- dim(spReturnsOffsetnn)[1]
    FMSE <- matrix(NA,P,Q+1)
    for (p in 1:P) for (q in 0:Q) {
    
    pr1  <- tryCatch(nnAR3(spReturnsOffsetnn[1:(T-1),1],p,q,nnAll[[p,q+1]]$weights)$pr_, error = function (e) e, warning = function(w) w)
    
    if(is(pr1,"warning") || is(pr1, "error")) {pr1<- nnAR3(spReturnsOffsetnn[1:(T-1),1], p, q, NULL)$pr_}
    
    pr2  <- tryCatch(nnAR3(spReturnsOffsetnn[1:(T-2),1],p,q,nnAll[[p,q+1]]$weights)$pr_, error = function(e) e, warning = function(w) w)
    
    if(is(pr2,"warning") || is(pr2, "error")) {pr2<- nnAR3(spReturnsOffsetnn[1:(T-2),1], p, q, NULL)$pr_}
    
    pr3  <- tryCatch(nnAR3(spReturnsOffsetnn[1:(T-3),1],p,q,nnAll[[p,q+1]]$weights)$pr_,error = function(e) e, warning = function(w) w)
    
    if(is(pr3,"warning") || is(pr3, "error")) {pr3<- nnAR3(spReturnsOffsetnn[1:(T-3),1], p, q, NULL)$pr_}
    
    FMSE[p,q+1] <- (as.numeric(spReturnsOffsetnn[T,1]) - pr1)^2 +
                     (as.numeric(spReturnsOffsetnn[(T-1),1]) - pr2)^2 +
                     (as.numeric(spReturnsOffsetnn[(T-2),1]) - pr3)^2
    
    nn  <- tryCatch(nnAR3(spReturnsOffsetnn[1:T,1],p,q,nnAll[[p,q+1]]$weights))
    if(is(nn,"warning") || is(nn, "error")) {nn<- nnAR3(spReturnsOffsetnn[1:T,1], p, q, NULL)}
    nnAll[[p,q+1]]=nn
    }
    p1 <- which(FMSE == min(FMSE), arr.ind = TRUE)[1]
    q1 <- which(FMSE == min(FMSE), arr.ind = TRUE)[2]
    
    nnOpt  <- nnAll[[p1,q1]]
    pr  <- nnOpt$pr_
    
    
    
    forecasts[d+1,1] = index(spReturnsOffset)[windowLength]
    forecasts[d+1,2] = ifelse(pr < 0, -1, 1)
    
  
  
   print(paste(paste('Date: ',index(spReturnsOffset)[windowLength],sep=''), paste(' Signal = ',ifelse(pr < 0, -1, 1),sep=''),paste(' Progress = ',paste(round(10000*d/foreLength)/100,'%',sep=''),sep=''), sep=";")) 

  }
write.csv(forecasts, file="forecastsnn.csv", row.names=FALSE, quote=FALSE) 
}
```

```{r}
forecastcsvnn <-read.csv(file="/users/zhangyuanyuan/desktop/R code/4/forecastsnn.csv", header=T, sep=",",dec = ".")

spnn2 <- as.xts(forecastcsvnn$V2,order.by=as.Date(forecastcsvnn$V1))
spnn2 <- lag(spnn2)
```

```{r}
spIntersectnn  <- merge( spnn2[,1], spReturns)
spnnReturns <- spIntersectnn[,1] * spIntersectnn[,2]
```


# Input the CSV file

```{r}
forecastcsv <-read.csv(file="C:/Users/zhang/Desktop/STAT GU4263/hw4/forecasts_prj1true.csv", header=T, sep=",",dec = ".")
forecastcsv1<-read.csv(file="C:/Users/zhang/Desktop/STAT GU4263/hw4/forecasts2.1.csv", header=T, sep=",",dec = ".")


spArimaGarch2 <- as.xts(forecastcsv$V2,order.by=as.Date(forecastcsv$V1))
spArimaGarch2 <- lag(spArimaGarch2)

spArimaGarch1 <- as.xts(forecastcsv1$V2,order.by=as.Date(forecastcsv1$V1))
spArimaGarch1 <- lag(spArimaGarch1)

```

# Create the ARIMA+GARCH and neural network returns

```{r}

spIntersect         <- merge( spArimaGarch2[,1], spReturns)
spArimaGarchReturns <- spIntersect[,1] * spIntersect[,2]

spIntersect1         <- merge( spArimaGarch1[,1], spReturns)
spArimaGarchReturns1 <- spIntersect1[,1] * spIntersect1[,2]
```

# Create the backtests for ARIMA+GARCH and neural network returns

```{r}

#merge the two time series of returns
spCombined <-merge(spArimaGarchReturns,spArimaGarchReturns1,all=F)
spCombined<-merge(spCombined,spIntersect[,2],all=F)
#exclude NA and compute cumulative log-returns 
spCombinedCurve   <-(1+cumsum(na.exclude(spCombined)))

```

# Plot the three time series of cumulative returns on one figure

```{r}
colnames(spCombinedCurve)<-c("neural network","Arma-Garch","Buy&Hold")
dygraph(spCombinedCurve) %>%
  dyRangeSelector()  %>% 
  dyOptions(axisLineWidth = 1.5, fillGraph = FALSE, drawGrid = FALSE, rightGap=50)
Loess_returns<-spArimaGarchReturns
colnames(Loess_returns)<-("S_P_ratio_Loess")
Sharpe_Ratio_Neural_Network<-sqrt(252)*(mean(Loess_returns,na.rm=T)/sd(Loess_returns,na.rm=T))
Sharpe_Ratio_Arma_Garch<-sqrt(252)*(mean(spArimaGarchReturns1,na.rm=T)/sd(spArimaGarchReturns1,na.rm=T))
```

#Report Sharpe Ratio of Buy and Hold
```{r}
Sharpe_Ratio_BuyandHold<-(mean(spIntersect[501:3232,2],na.rm=T)/sd(spIntersect[501:3232,2],na.rm=T))*sqrt(252)
Sharpe_Ratio_BuyandHold
```

#Report Sharpe Ratio of Neural Network
```{r}
Sharpe_Ratio_Neural_Network
```

#Report Sharpe Ratio of ARMA-GARCH
```{r}
Sharpe_Ratio_Arma_Garch
```

#Since the cumulative returns of ARMA-GARCH and Sharpe Ratio of Arma Garch are both higher, ARMA-GARCH is a better strategy.
