---
title: "Return Analysis of High Frequency Strategy"
author: "Han Zhang"
date: "Dec 1, 2016"
output: html_document
---
```{r, eval=TRUE, include=FALSE}
library("xts") #for time series
library("nloptr") #for optimization
library(zoo)
library("dygraphs") #for plots
library("magrittr") # pipes
library(dplyr)
#library(streamgraph)
library(viridis)

library(quantmod)
library(lattice)
library(timeSeries)
library(rugarch)
library(neuralnet)
```

```{r}
r_NN<-read.csv(file="C:/Users/zhang/Desktop/STAT GU4263/r_NN_HFdata.csv", header=T, sep=",",dec = ".")
r_LS<-read.csv(file="C:/Users/zhang/Desktop/STAT GU4263/project/r_LS_HFdata.csv", header=T, sep=",",dec = ".")
r_AG<-read.csv(file="C:/Users/zhang/Desktop/STAT GU4263/project/r_AG_HFdata.csv", header=T, sep=",",dec = ".")

```

```{r, eval=TRUE, include=FALSE}
r_NN<-t(r_NN)
r_LS<-t(r_LS)
r_AG<-t(r_AG)
```



#compute cumulative log return of every day and store it at last column (which is all NA before)
```{r}
for (i in 1:dim(r_NN)[1]){
  r_NN[i,151]<-sum(r_NN[i,(1:150)])
  r_AG[i,151]<-sum(r_AG[i,(1:150)])
  r_LS[i,151]<-sum(r_LS[i,(1:150)])
}
```

#compute gross cumulative returns
```{r}
r_sum_NN<-r_NN[,151]
r_sum_AG<-r_AG[,151]
r_sum_LS<-r_LS[,151]

data <- read.csv("C:/Users/zhang/Desktop/STAT GU4263/project/dataHW5csv.csv")  # read csv file 
prices1min <- t(data[,3:393])

data_df <- data.frame(data[,2:393])
row.names(data_df) <- data[,1]
data_df <- data_df[complete.cases(data_df),]
data_df <- xts(data_df,order.by = as.Date(row.names(data_df),format = '%m/%d/%Y'))


returns1min <- 100*diff(log(t(data_df[,2:392])))
returns1min <- t(returns1min)
returns1min <- xts(returns1min,order.by = as.Date(index(data_df)),format = '%m/%d/%Y')
returns1min <- returns1min[complete.cases(returns1min),]

returns1min<-returns1min[,241:390] #question:buy and hold start at the beginning of the day?
r_sum_buyhold<-rep(NA,650)
for (i in 1:650){
r_sum_buyhold[i]<-sum(returns1min[i,])
}

gross_LS<-rep(NA,650)
gross_AG<-rep(NA,650)
gross_buyhold<-rep(NA,650)
gross_NN<-rep(NA,650)

for (i in 1:650){
  gross_LS[i]<-exp(sum(r_sum_LS[1:i])/100)
  gross_NN[i]<-exp(sum(r_sum_NN[1:i])/100)
  gross_AG[i]<-exp(sum(r_sum_AG[1:i])/100)
  gross_buyhold[i]<-exp(sum(r_sum_buyhold[1:i])/100)
}


gross_LS<-xts(gross_LS,order.by=index(returns1min))
gross_NN<-xts(gross_NN,order.by=index(returns1min))
gross_AG<-xts(gross_AG,order.by=index(returns1min))

gross<-merge(gross_LS,gross_NN,gross_AG,gross_buyhold)
colnames(gross)<-c("Loess Method","Neural Network","Arma-Garch","Buy&Hold")
```

#Plot gross cumulative returns of each strategy and buy and hold 
```{r}
dygraph(gross,ylab="million dollars")
```


#Compute Sharpe Ratios 
```{r}
SR_NN<-sqrt(252)*mean(r_sum_NN)/sd(r_sum_NN)
SR_LS<-sqrt(252)*mean(r_sum_LS)/sqrt(var(r_sum_LS))
SR_buyhold<-sqrt(252)*mean(r_sum_buyhold)/sqrt(var(r_sum_buyhold))
SR_AG<-sqrt(252)*mean(r_sum_AG)/sqrt(var(r_sum_AG))

```

#Annualized Sharpe Ratios of Arma-Garch Model for 
```{r}
SR_AG
```

#Annualized Sharpe Ratios of Neural Network Model 
```{r}
SR_NN
```

#Annualized Sharpe Ratios of Loess Model
```{r}
SR_LS
```

#Annualized Sharpe Ratios of Buy and Hold 
```{r}
SR_buyhold
```


<br>


```{r}

fore_NN<-read.csv(file="C:/Users/zhang/Desktop/STAT GU4263/forecasts_NN_HFdata.csv", header=T, sep=",",dec = ".")
fore_LS<-read.csv(file="C:/Users/zhang/Desktop/STAT GU4263/project/forecasts_LS_HFdata.csv", header=T, sep=",",dec = ".")
fore_AG<-read.csv(file="C:/Users/zhang/Desktop/STAT GU4263/project/forecasts_AG_HFdata.csv", header=T, sep=",",dec = ".")
```

```{r, eval=TRUE, include=FALSE}
fore_NN<-t(fore_NN)
fore_LS<-t(fore_LS)
fore_AG<-t(fore_AG)
```

```{r}
accumulated_wealth<-matrix(nrow=650,ncol=150)
cumulative_previous<-1000000
number<-0
for(d in 1:650){
  transaction_cost<-as.numeric(data_df[index(gross_AG[d,]),1])
  
  for (m in 1:149){
    accumulated_wealth_temp<-cumulative_previous*exp(r_AG[d,m]/100)
    if(fore_AG[d,m]!=fore_AG[d,(m+1)]){
      number=number+1
      accumulated_wealth_temp<-accumulated_wealth_temp*(1-transaction_cost)
    }
    accumulated_wealth[d,m]<-accumulated_wealth_temp
    cumulative_previous<-accumulated_wealth_temp
  }
  accumulated_wealth[d,150]<-(accumulated_wealth[d,149])*(exp(r_AG[d,150]/100))*(1-transaction_cost)
  cumulative_previous<-accumulated_wealth[d,150]
}


accumulated_wealth_NN<-matrix(nrow=650,ncol=150)
cumulative_previous<-1000000
number<-0
for(d in 1:650){
  transaction_cost<-as.numeric(data_df[index(gross_NN[d,]),1])
  
  for (m in 1:149){
    accumulated_wealth_temp<-cumulative_previous*exp(r_NN[d,m]/100)
    if(fore_NN[d,m]!=fore_NN[d,(m+1)]){
      number=number+1
      accumulated_wealth_temp<-accumulated_wealth_temp*(1-transaction_cost)
    }
    accumulated_wealth_NN[d,m]<-accumulated_wealth_temp
    cumulative_previous<-accumulated_wealth_temp
  }
  accumulated_wealth_NN[d,150]<-(accumulated_wealth_NN[d,149])*(exp(r_NN[d,150]/100))*(1-transaction_cost)
  cumulative_previous<-accumulated_wealth_NN[d,150]
}

accumulated_wealth_LS<-matrix(nrow=650,ncol=150)
cumulative_previous<-1000000
number<-0
for(d in 1:650){
  transaction_cost<-as.numeric(data_df[index(gross_LS[d,]),1])
  
  for (m in 1:149){
    accumulated_wealth_temp<-cumulative_previous*exp(r_LS[d,m]/100)
    if(fore_LS[d,m]!=fore_LS[d,(m+1)]){
      number=number+1
      accumulated_wealth_temp<-accumulated_wealth_temp*(1-transaction_cost)
    }
    accumulated_wealth_LS[d,m]<-accumulated_wealth_temp
    cumulative_previous<-accumulated_wealth_temp
  }
  accumulated_wealth_LS[d,150]<-(accumulated_wealth_LS[d,149])*(exp(r_LS[d,150]/100))*(1-transaction_cost)
  cumulative_previous<-accumulated_wealth_LS[d,150]
}

accumulated_wealth_buyhold<-matrix(nrow=650,ncol=150)
cumulative_previous<-1000000
for(d in 1:650){
  transaction_cost<-as.numeric(data_df[index(gross_LS[d,]),1])
  
  for (m in 1:149){
    accumulated_wealth_temp<-cumulative_previous*exp(returns1min[d,m]/100)
    
    accumulated_wealth_buyhold[d,m]<-accumulated_wealth_temp
    cumulative_previous<-accumulated_wealth_temp
  }
  accumulated_wealth_buyhold[d,150]<-(accumulated_wealth_buyhold[d,149])*(exp(returns1min[d,150]/100))*(1-transaction_cost)
  cumulative_previous<-accumulated_wealth_buyhold[d,150]
}
#compute net cumulative returns of each strategy
accumulated_AG<-(accumulated_wealth[,150]-1000000)/1000000
accumulated_AG<-xts(accumulated_AG,order.by=index(returns1min))
accumulated_NN<-xts((accumulated_wealth_NN[,150]-1000000)/1000000,order.by=index(returns1min))
accumulated_LS<-xts((accumulated_wealth_LS[,150]-1000000)/1000000,order.by=index(returns1min))
accumulated_buyhold<-xts((accumulated_wealth_buyhold[,150]-1000000)/1000000,order.by=index(returns1min))

accumulated<-merge(accumulated_AG,accumulated_NN,accumulated_buyhold,accumulated_LS)
colnames(accumulated)<-c("Arma_Garch","Neural Network","Buy&Hold","Loess Method")
```

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

#Plot the net cumulative returns of each strategy and buy and hold
```{r}
dygraph(accumulated)
```



```{r}
logreturn_AG_c<-log(accumulated_AG+1)
logreturn_NN_c<-log(accumulated_NN+1)
logreturn_LS_c<-log(accumulated_LS+1)
logreturn_buyhold_c<-log(accumulated_buyhold+1)
logreturn_AG<-as.numeric(logreturn_AG_c[1])
logreturn_NN<-as.numeric(logreturn_NN_c[1])
logreturn_LS<-as.numeric(logreturn_LS_c[1])
logreturn_buyhold<-as.numeric(logreturn_buyhold_c[1])
for (i in 2:650){
  logreturn_AG_temp<-as.numeric(logreturn_AG_c[i])-as.numeric(logreturn_AG_c[i-1])
  logreturn_NN_temp<-as.numeric(logreturn_NN_c[i])-as.numeric(logreturn_NN_c[i-1])
  logreturn_LS_temp<-as.numeric(logreturn_LS_c[i])-as.numeric(logreturn_LS_c[i-1])
  logreturn_buyhold_temp<-as.numeric(logreturn_buyhold_c[i])-as.numeric(logreturn_buyhold_c[i-1])
  logreturn_AG<-rbind(logreturn_AG,logreturn_AG_temp)
  logreturn_NN<-rbind(logreturn_NN,logreturn_NN_temp)
  logreturn_LS<-rbind(logreturn_LS,logreturn_LS_temp)
  logreturn_buyhold<-rbind(logreturn_buyhold,logreturn_buyhold_temp)
}
```
  
#Compute Sharpe ratios 
```{r}
SR_AG_1<-sqrt(252)*mean(logreturn_AG)/(sd(logreturn_AG))
SR_NN_1<-sqrt(252)*mean(logreturn_NN)/(sd(logreturn_NN))
SR_LS_1<-sqrt(252)*mean(logreturn_LS)/(sd(logreturn_LS))
SR_buyhold_1<-sqrt(252)*mean(logreturn_buyhold)/(sd(logreturn_buyhold))
```  
  
  
#Annualized Sharpe Ratios of Arma-Garch Model 
```{r}
SR_AG_1
```

#Annualized Sharpe Ratios of Neural Network Model for 
```{r}
SR_NN_1
```

#Annualized Sharpe Ratios of Loess Model for 
```{r}
SR_LS_1
```

#Annualized Sharpe Ratios of Buy and Hold for 
```{r}
SR_buyhold_1
```

<br>


```{r}
net_pl_AG<-rep(NA,650)
net_pl_NN<-rep(NA,650)
net_pl_buyhold<-rep(NA,650)
net_pl_LS<-rep(NA,650)
for (i in 1:650){
  net_pl_AG[i]<-(accumulated_wealth[i,150]-accumulated_wealth[i,1])
  net_pl_NN[i]<-(accumulated_wealth_NN[i,150]-accumulated_wealth_NN[i,1])
  net_pl_buyhold<-(accumulated_wealth_buyhold[i,150]-accumulated_wealth_buyhold[i,1])
  net_pl_LS[i]<-(accumulated_wealth_LS[i,150]-accumulated_wealth_LS[i,1])
  
}
```


```{r, eval=TRUE, include=FALSE}
setwd('C:/Users/zhang/Desktop/STAT GU4263')


price_data <- read.csv("C:/Users/zhang/Desktop/STAT GU4263/data/data/dataHW5csv.csv",sep=",")


first_day<-t(price_data[1,(3:dim(price_data)[2])])
log_return <- 100*(diff(log(first_day)))

for (k in 2:dim(price_data)[1])
{
  day_price<-t(price_data[k,(3:dim(price_data)[2])])
  log_return_day<-100*(diff(log(day_price)))

  log_return<-cbind(log_return,log_return_day)
}

colnames(log_return)<-price_data[,1]


log_returns<-price_data
for( i in 1:dim(price_data)[1]){
  log_returns[i,3]<-NA
  log_returns[i,4:(dim(price_data)[2])]<-t(log_return[,i])
}


pacf_all<-pacf(log_return[,1],lag.max=10,na.action=na.pass,plot=FALSE)$acf

for (i in 2:dim(log_return)[2]){
  pacf_day<-pacf(log_return[,i],lag.max=10,na.action=na.pass,plot=FALSE)$acf
  pacf_all<-cbind(pacf_all,pacf_day)
}

colnames(pacf_all)<-price_data[,1]
pacf_all<-t(pacf_all)


open_price<-as.data.frame(price_data[,3])
close_price<-as.data.frame(price_data[,dim(price_data)[2]])
low_price<-min(price_data[1,(3:dim(price_data)[2])])
high_price<-max(price_data[1,(3:dim(price_data)[2])])

for (i in 2:dim(price_data)[1]){
  low_price_day<-min(price_data[i,(3:dim(price_data)[2])])
  high_price_day<-max(price_data[i,(3:dim(price_data)[2])])
  low_price<-rbind(low_price,low_price_day)
  high_price<-rbind(high_price,high_price_day)
}

rownames(open_price)<-price_data[,1]
rownames(low_price)<-price_data[,1]
rownames(high_price)<-price_data[,1]
rownames(close_price)<-price_data[,1]

D<-as.Date.factor(price_data[,1],"%m/%d/%Y")
sigma<-as.data.frame(rep(NA,dim(price_data)[1]))
for (i in 2:dim(price_data)[1]){
  if(!is.nan(open_price[i,]) &  !is.nan(close_price[(i-1),])){
    if(open_price[i,]!=0  &close_price[(i-1),]!=0){
  sigma_tiuda<-0.5*((high_price[i,]-low_price[i,])^2)-(2*log(2)-1)*((close_price[i,]-open_price[i,])^2)
  sigma[i,]<-(0.12/0.66)*((open_price[i,]-close_price[(i-1),])^2)+(0.88*sigma_tiuda)/(1-0.66)
  }
  }
}
volatility<-sqrt(sigma)
volatility_xts <- xts(volatility,order.by = D)
volatility_xts<-lag(volatility_xts)
```


#Plot net profits & losses of ARMA-GARCH model against previous day volatility estimates
```{r}
net_pl_AG<-xts(net_pl_AG,order.by=index(returns1min))
plot_AG<-merge(volatility_xts,net_pl_AG)
plot_AG <- plot_AG[complete.cases(plot_AG),]
colnames(plot_AG)<-c("volatility","net profits&losses of Arma-Garch")
scatter.smooth(plot_AG)
```

#Plot net profits & losses of Neural Network model against previous day volatility estimates
```{r}
net_pl_NN<-xts(net_pl_NN,order.by=index(returns1min))
plot_NN<-merge(volatility_xts,net_pl_NN)
plot_NN <- plot_NN[complete.cases(plot_NN),]
colnames(plot_NN)<-c("volatility","net profits & losses of Neural Network")
scatter.smooth(plot_NN)
```

##Plot net profits & losses of Loess Method against previous day volatility estimates
```{r}
net_pl_LS<-xts(net_pl_LS,order.by=index(returns1min))
plot_LS<-merge(volatility_xts,net_pl_LS)
plot_LS <- plot_LS[complete.cases(plot_LS),]
colnames(plot_LS)<-c("volatility","net profits& losses of Loess Method")
scatter.smooth(plot_LS)
```